The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms

### 2017-12-09 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
did some diagnostics on the CI not even problem
To me it’s not a specification problem. It’s either a bootstrap
calculation problem or a plotting problem.
Revert "added new figures and new FEV to presentation"
This reverts commit ecb61e558c0db68064b3e62886e566b729a7b87e.

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Impulse responses to a news shock}

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_36}
\end{figure}

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Impulse responses to an IT shock}

\vspace{-1cm}
\noindent
\begin{figure}
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_47}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{TFP response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_04}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_13}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Real SP500 response to both shocks}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_06}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_14}
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Other responses to  both shocks}

\begin{figure}
\begin{multicols}{2}
\centering
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_07}\\  
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_09}\\ 
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_10}\\ 
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_05-Dec-2017_10_53_11}\\

\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_15}\\
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_16}\\
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_17}\\ 
\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_05-Dec-2017_10_53_19}\\

\end{multicols}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
